---
title: "Manuscript"
subtitle: "Malawi Hospital Air Quality Data"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r}
library(readr)
library(dplyr)
library(DT)
library(forcats)
library(lubridate)
```

```{r}

dat_in <- read_csv(here::here("data/intermediate/malawi-hospitals-air-quality"))

vec_hospital_id <- dat_in %>% 
  count(id) %>% 
  pull(id)

vec_hospital_name <- dat_in %>% 
  count(location) %>% 
  pull(location)


```

```{r}

# Data transformation

usepa_level_fct <- c("Good", 
                     "Moderate", 
                     "Unhealthy for Sensitive Groups", 
                     "Unhealthy", 
                     "Very Unhealthy", 
                     "Hazardous")

# Data transformation

dat_air_quality <- dat_in %>% 
  mutate(air_quality = case_when(
    indicator == "pm2.5" & value <= 12 ~ "Good",
    indicator == "pm2.5" & value > 12 & indicator == "pm2.5" & value <= 35.4 ~ "Moderate",
    indicator == "pm2.5" & value > 35.4 & indicator == "pm2.5" & value <= 55.4 ~ "Unhealthy for Sensitive Groups",
    indicator == "pm2.5" & value > 55.4 & indicator == "pm2.5" & value <= 150.4 ~ "Unhealthy",
    indicator == "pm2.5" & value > 150.4 & indicator == "pm2.5" & value <= 250.4 ~ "Very Unhealthy",
    indicator == "pm2.5" & value > 250.4 ~ "Hazardous",
    indicator == "pm10" & value <= 54.9 ~ "Good",
    indicator == "pm10" & value > 54.9 & indicator == "pm10" & value <= 154.9 ~ "Moderate",
    indicator == "pm10" & value > 154.9 & indicator == "pm10" & value <= 254.9 ~ "Unhealthy for Sensitive Groups",
    indicator == "pm10" & value > 254.9 & indicator == "pm10" & value <= 354.9 ~ "Unhealthy",
    indicator == "pm10" & value > 354.9 & indicator == "pm10" & value <= 424.9 ~ "Very Unhealthy",
    indicator == "pm10" & value > 424.9 ~ "Hazardous",
  )) %>% 
  mutate(air_quality =
                    fct_relevel(air_quality, 
                                levels = usepa_level_fct)) 
```

# Introduction

The purpose of this document is to perform some initial exploratory data analysis for air quality data from Malawi. Based on this analysis, in-depth analysis will be performed and publication ready figures can be produced. 

# Data 

Air quality data (PM2.5 and PM10) was collected in roughly 5-minute intervals from eight locations at one hospital. The locations are `r knitr::combine_words(vec_hospital_name)`.

One sensor was installed at each location, either on the side or on the outside wall. 

# Data Exploration

- 24 hour average
- baseline (not the two peaks)
- Hourly average
- Exposure in categories of hazard
- Peaks over 500 a day
- Difference between indoor and outdoor sensors
- Ratios PM10 / PM25 (differences by location)
	- Indicator for composition of waste that is being burned
	- Guardian shelter
		- Shed/barn where guardians sleep at night
		- 40 women cooking with charcoal inside the barn
		
```{r}

yr_vec <- dat_clean %>% 
  #filter(location == "6B") %>% 
  mutate(year = year(date)) %>% 
  count(year) %>% 
  filter(year != 2019) %>% 
  pull(year)

dat_clean %>% 
    mutate(year = year(date)) %>% 
  filter(year %in% yr_vec)

  ggplot(aes(x = date, y = value, color = indicator)) +
  geom_line() 


dat_clean %>% 
  ggplot(aes(x = date, y = value, color = indicator)) +
  geom_line() +
  facet_wrap(~location, ncol = 1)
  
```



